The 2014 SMT Competition

### 2015-08-03 2014/report/SMTCOMP.tex
Minor.

The competition is sponsored by the SMT workshop, which was held in conjunction with the
CAV, IJCAR, and SAT conferences at FLoC 2014~\cite{FLoC2014}, at the Vienna Summer of Logic~\cite{VSL} in July 2014.
Information about the winners
and results of the competition is summarized in this report and is available online at \url{www.smtcomp.org}; information
about previous years' competitions is also available at that website and in published summary reports~\cite{springerlink:10.1007/s10817-012-9246-5,DBLP:conf/cade/CokGBD12,it:2014-017}.

@@

In planning the 2014 competition, the organizers' overall goal was to encourage breadth
in the capability of SMT solvers. SMT-COMP 2014 benefited from the evaluation that was performed in 2013 and the experience of previous competitions. As a result we established the following emphases. Note that, as described in later sections, the competition is
divided into a number of divisions, each focuses on a given logic and each with its own set of benchmark problems and solvers.
\begin{itemize}
\item In 2012 the competition was narrowed to a smaller number of more significant logics. In response to feedback, in 2014 we reverted to the practice of evaluating solvers in all available divisions.
\item A significant result of the 2013 Evaluation was that the result of a competition was highly sensitive to the selection of benchmarks: different random selections of benchmarks resulted in different winning orders in a large fraction of samples. Hence, an aim for 2014 was to use as large a benchmark set as possible in the competition to minimize this effect. We were able to run the competition with all eligible benchmarks. This point is discussed further in \S\ref{sec:benchmark-selection}
\item In 2012 some experimental tracks were held: parallel performance, unsat cores, and proof generation. The participation in those tracks was light. Since in 2014 we also had to migrate to using the new StarExec cluster to execute the competition, we held only a main track and an application (incremental) track in the 2014 competition. The organizers still appreciate the value of measuring the performance of solvers on new features such as model generation, unsat core determination, and proof generation, and recommend that they be reinstated in some future edition of the competition.
\item A significant change in 2014 was to increase the timeout limit for a solver processing a given benchmark from 25 minutes (in 2012) to 40 minutes (see \S\ref{sec:procedure} for details on the competition parameters and \S\ref{sec:timeouts} for a discussion on their effects).

@@

\section{SMT-LIB logic, language and solvers}
\label{sec:context}

@@

The log scaling of the scores for each division is a somewhat arbitrary means to adjust the scores for the wide variety of numbers of benchmarks. If each division is treated equally, with a score, say, of 1.0 for the division for solving all the benchmarks in the division correctly, then the benchmarks for small divisions would count significantly more toward a composite score than those of divisions with many benchmarks. On the other hand, counting each benchmark equally appeared to underweight the effect of a solver's effort to participate in multiple divisions. The log scaling seemed a reasonable compromise between linearly combining numbers of benchmarks these two extremes. Similarly, the square of the fraction successfully solved is an
approximate mechanism to give more weight to solving the harder problems than the easier.

>>>>

The competition is sponsored by the SMT workshop, which was held in conjunction with the
CAV, IJCAR, and SAT conferences at FLoC 2014~\cite{FLoC2014}, at the Vienna Summer of Logic~\cite{VSL} in July 2014.
Information about the winners
and results of the competition is summarized in this report and is available online at \url{www.smtcomp.org}.  Information
about previous years' competitions is also available at that website and in published summary reports~\cite{springerlink:10.1007/s10817-012-9246-5,DBLP:conf/cade/CokGBD12,it:2014-017}.

@@

In planning the 2014 competition, the organizers' overall goal was to encourage breadth in the capability of SMT solvers.  SMT-COMP 2014 benefited from the evaluation that was performed in 2013 and the experience of previous competitions.  As a result we established the following emphases.  Note that, as described in later sections, the competition is divided into a number of divisions, each focuses on a given logic, and each has its own set of benchmark problems and solvers.
\begin{itemize}
\item In 2012 the competition was narrowed to a smaller number of more significant logics. In response to feedback, in 2014 we reverted to the practice of evaluating solvers in all available divisions.
\item A significant result of the 2013 Evaluation was that the results of previous competitions were highly sensitive to the selection of benchmarks: different random selections of benchmarks resulted in different winning orders in a large fraction of samples. Hence, an aim for 2014 was to use as large a benchmark set as possible in the competition to minimize this effect. We were able to run the competition with all eligible benchmarks. This point is discussed further in~\S\ref{sec:benchmark-selection}.
\item In 2012 some experimental tracks were held: parallel performance, unsat cores, and proof generation. The participation in those tracks was light. Since in 2014 we also had to migrate to using the new StarExec cluster to execute the competition, we held only a main track and an application (incremental) track in the 2014 competition. The organizers still appreciate the value of measuring the performance of solvers on new features such as model generation, unsat core determination, and proof generation, and recommend that these tracks be reinstated in some future edition of the competition.
\item A significant change in 2014 was to increase the timeout limit for a solver processing a given benchmark from 25 minutes (in 2012) to 40 minutes (see \S\ref{sec:procedure} for details on the competition parameters and \S\ref{sec:timeouts} for a discussion on their effects).

@@

\section{SMT-LIB Logic, Language and Solvers}
\label{sec:context}

@@

The log scaling of the scores for each division is a somewhat arbitrary means to adjust the scores for the wide variety of numbers of benchmarks. If each division is treated equally, with a score, say, of 1.0 for the division for solving all the benchmarks in the division correctly, then the benchmarks for small divisions would count significantly more toward a composite score than those of divisions with many benchmarks. On the other hand, counting each benchmark equally appeared to underweight the effect of a solver's effort to participate in multiple divisions. The log scaling seemed a reasonable compromise between these two extremes. Similarly, the square of the fraction successfully solved is an approximate mechanism to give more weight to solving the harder problems.
